State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-04-14 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex

\end{algorithmic}
\end{algorithm}
\section{Results}
We simulated a neural field to the generate data used in the state and parameter estimation. An example of the simulated field can be seen in Figure~\ref{}. The Figure demonstrates the experimental design where the sensors were placed in the centre of the field.

>>>>

\end{algorithmic}
\end{algorithm}
\section{Results}
We simulated a neural field to the generate data used in the state and parameter estimation. All parameters for the model are given in Table~\ref{}. An example of the simulated field can be seen in Figure~\ref{} A. The Figure demonstrates the experimental design where the sensors were placed in the centre of the field. This design allowed for uncertainty around the edges of the sensor array, which would be typical from physical data, and alleviated problems associated with boundary conditions. Figure~\ref{} B. shows example data from the sensors of the model, and Figure~\ref{} C. shows the power spectral density of on of the simulated time-series. The PSD shows the typical $1/f$ characteristics of intracranial EEG.
